Boccaccio example: end to end truth for California Current

### 2019-05-24 FullBoccaccioTruthEx.Rmd
with calc true age saved not plotted yet

@@

```{r testagecl}
# add YOY file to the config files
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

@@

trueagesall_ss <- calc_stage2age(nums_data = Natage_ss,
                                 biolprm = biol, 
                                 yoy = YOY,
                                 fgs = funct.groups, 
                                 runprm = runpar)

>>>>

This is Bocaccio true age class output. However, the 10 standard atlantis age classes aggregate 5 true ages each for Bocaccio.

@@

```{r testagecl, eval=FALSE}
# add YOY file to the config files
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

@@

trueagesall <- calc_stage2age(nums_data = truth$nums,
                                 biolprm = biol, 
                                 yoy = YOY,
                                 fgs = funct.groups, 
                                 runprm = runpar)

saveRDS(trueagesall, file.path(d.name, paste0(scenario.name, "Nattrueagecensus.rds")) )

These should be true age comps for Bocaccio in annual ages:

```{r plotannage}

trueNatage <- readRDS(file.path(d.name, paste0(scenario.name, "Nattrueagecensus.rds")))

# run survey  and sample fish on this for completeness?

# plot it
